---
title: "Make Me A Star"
subtitle: "US Manufactures"
author: "Clare Gibson"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
    toc_float: true
    theme: cosmo
    code_folding: show
---

```{r setup, include=FALSE}
# Load packages
library(knitr)

# Knitr Options
opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	fig.align = 'center'
)
```

# Packages
The following packages are used in this notebook: `tidyverse`, `lubridate`.
```{r load-packages}
library(tidyverse)      # for general wrangling
library(lubridate)      # for date wrangling
```

# The Dataset
The dataset I will be using for this example comes from the [United States Census Bureau](https://www.census.gov/) and summarizes [survey data](https://data.census.gov/cedsci/table?q=AM1831BASIC&tid=ASMAREA2017.AM1831BASIC01&hidePreview=true) asked of manufacturing firms in 2018 and 2019. It contains a variety of measures concerning payroll and numbers of employees for several industries according to the North American Industry Classification System (or [NAICS](https://www.census.gov/naics/)). In the course of this project, I will extend this dataset with geography, time, and other dimension tables.

# Loading the Data
I will start by loading the NAICS manufacturing dataset.
```{r load-manufacturing-data}
# Read the manufacturing data into a df
manu <- read_csv("data-in/manufacturing_data.csv")

# Display the head
manu %>% 
  head(5) %>% 
  kable(align = "l",
        caption = "Head of the manufacturing dataset")
```

